Area maximisation in continuous time

### 2013-11-12 Notes/ContTime.tex
bootstrap envelope

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\eq}{\mathbf{p}^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\uv}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{q}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Area maximisation in continuous time}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

Therefore the bound must be saturated exactly once and $\mu(s)=\mu_0\,\delta(s-s_0)$.
Now \eqref{eq:envI}, \eqref{eq:envq} and \eqref{eq:envKT} read
%
\begin{equation}\label{eq:satonce}
  \mu_0 = (q+s_0)\,\e^{-qt_0},
  \qquad
  (q+s_0)t_0 = 1,
  \qquad
  \CI = \frac{B(s_0)}{t_0}.
\end{equation}
%
This satisfies \eqref{eq:envKTm}.
Now \eqref{eq:envKTbnd} tells us
%
\begin{equation}\label{eq:satoncebnd}
\begin{aligned}
  B(s) \geq \frac{B(s_0)}{(q+s)t_0}, 
  \qquad\text{or}\qquad
  1 + (s-s_0)t_0 \geq \frac{C(s)}{C(s_0)}.
\end{aligned}
\end{equation}
%
As the two sides are equal at $s=s_0$, it is necessary that they touch tangentially for this bound to be true elsewhere.
The linearity of the LHS and concavity of the RHS ensure that this is sufficient for the bound to be satisfied for all $s$.
This condition is
%
\begin{equation}\label{eq:envs0t0}
  t_0 = \frac{C'(s_0)}{C(s_0)}.
\end{equation}
%

The resulting SNR curve and envelope are
%
\begin{equation}\label{eq:env}
  \snr(t) = \frac{\sqrt{N}\,\e^{(s_0-1/t_0)t}}{C'(s_0)},
  \qquad
  \snr(t_0) = \frac{\sqrt{N}\,\e^{s_0t_0-1}}{C'(s_0)},
\end{equation}
%
where $s_0$ is a function of $t_0$ determined by \eqref{eq:envs0t0}.

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\eq}{\mathbf{p}^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\uv}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{q}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Area maximisation in continuous time}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

Therefore the bound must be saturated exactly once and $\mu(s)=\mu_0\,\delta(s-s_0)$.
Now \eqref{eq:envI}, \eqref{eq:envq} and \eqref{eq:envKT} read
%
\begin{equation}\label{eq:satonce}
  \mu_0 = (q+s_0)\,\e^{-qt_0},
  \qquad
  (q+s_0)t_0 = 1,
  \qquad
  \CI = \frac{B(s_0)}{t_0}.
\end{equation}
%
This satisfies \eqref{eq:envKTm}.
Now \eqref{eq:envKTbnd} tells us
%
\begin{equation}\label{eq:satoncebnd}
\begin{aligned}
  B(s) \geq \frac{B(s_0)}{(q+s)t_0},
  \qquad\text{or}\qquad
  1 + (s-s_0)t_0 \geq \frac{C(s)}{C(s_0)}.
\end{aligned}
\end{equation}
%
As the two sides are equal at $s=s_0$, it is necessary that they touch tangentially for this bound to be true elsewhere.
The linearity of the LHS and concavity of the RHS ensure that this is sufficient for the bound to be satisfied for all $s$.
This condition is
%
\begin{equation}\label{eq:envs0t0}
  t_0 = \frac{C'(s_0)}{C(s_0)} = -\frac{B'(s_0)}{B(s_0)}.
\end{equation}
%

The resulting SNR curve and envelope are
%
\begin{equation}\label{eq:env}
  \snr(t) = \frac{\sqrt{N}\,\e^{(s_0-1/t_0)t}}{C'(s_0)},
  \qquad
  \snr(t_0) = \sqrt{N}\env(t_0) = \frac{\sqrt{N}\,\e^{s_0t_0-1}}{C'(s_0)}
   = \frac{\sqrt{N}\,B(s)\e^{s_0t_0-1}}{t_0},
\end{equation}
%
where $s_0$ is a function of $t_0$ determined by \eqref{eq:envs0t0}.

\subsection{Bootstrap}\label{sec:boot}

Using the upper bounds on initial SNR and area, we can derive the following envelope:
%
\begin{equation}\label{sec:envinitarea}
  \env_0(t_0) =
    \begin{cases}
    \e^{-rt_0/(M-1)},    & rt_0 \leq M-1,\\
    \frac{M-1}{\e rt_0}, & rt_0 \geq M-1.
    \end{cases}
    =
    \begin{cases}
    \e^{-\rh t_0},        & \rh t_0 \leq 1,\\
    \frac{1}{\e \rh t_0}, & \rh t_0 \geq 1.
    \end{cases}
\end{equation}
%
We will use the notation $\rh=r/(M-1)$ in this subsection.
As no memory curve can cross this, the Laplace transform of any model's memory curve must be smaller than
%
\begin{equation}\label{eq:envlt}
\begin{aligned}
  \frac{A(s)}{\sqrt{N}} \leq B(s) < B_0(s) &= \intd[_0^\infty]{t_0} \e^{-st_0}\env(t_0) \\
   &= \intd[_0^{1/\rh}]{t_0} \e^{-(s+\rh)t_0}
   + \intd[_{1/\rh}^\infty]{t_0} \frac{\e^{-st_0-1}}{\rh t_0} \\
   &= \frac{1-\e^{-s/\rh-1}}{s+\rh} + \ldots
\end{aligned}
\end{equation}
%
This loose bound can be used to derive a new envelope
%
\begin{equation}\label{eq:envb0}
  \env_1(t_0) = \frac{B_0(s_0) \e^{s_0t_0-1}}{t_0} = \ldots
  \qquad t_0 = -\frac{B_0'(s_0)}{B_0(s_0)}. 
\end{equation}
%
As there are additional constraints, $\env_1(t_0) \leq \env_0(t_0)$.
This can be Laplace-transformed to get a better bound, $B_1(s) \leq B_0(s)$, which can then be used to get an even better envelope.

This procedure can be iterated an arbitrary number of times
%
\begin{equation}\label{eq:bootiter}
  B_k(s) = \intd[_0^\infty]{t_0} \e^{-st_0}\env_k(t_0),
  \qquad
  \env_{k+1}(t_0)=\frac{B_k(s_0) \e^{s_0t_0-1}}{t_0},
  \quad t_0 = -\frac{B_k'(s_0)}{B_k(s_0)}.
\end{equation}
%
This will end at the fixed point
%
\begin{equation}\label{eq:bootfixedpt}
  B_\infty(s) = \intd[_0^\infty]{t_0} \e^{-st_0}\env_\infty(t_0),
  \qquad
  \env_\infty(t_0)=\frac{B_\infty(s_0) \e^{s_0t_0-1}}{t_0},
  \quad t_0 = -\frac{B_\infty'(s_0)}{B_\infty(s_0)}.
\end{equation}
%
We can eliminate $\env_\infty$ and $t_0$ (assuming that $s_0\to \infty$ as $t_0 \to 0$ and vice versa) to get the following integro-differential equation:
%
\begin{equation}\label{eq:bootbnd}
  B_\infty(s) = \intd[_0^\infty]{s_0} \e^{(s-s_0)B'_\infty(s_0)/B_\infty(s_0)} 
      \brk{B'_\infty(s_0)-\frac{B_\infty(s_0)B''_\infty(s_0)}{B'_\infty(s_0)}}.
\end{equation}
%

Because actual memory curves can, at best, touch the envelope at one time, there will always be a significant gap between the laplace transforms of the memory curves and of the envelope.
Therefore both the bound $B_\infty(s)$ and the envelope $\env_\infty(t_0)$ will be loose.
